---
title: "Project Check-In"
author: "Andrew Sandico, Abraham Yang, Hope Huang, Mahmoud Ghanem, Mark Haase"
date: "10/26/2023"
geometry: margin=0.5in
output:
  pdf_document:
    number_sections: yes
classoption: a3paper
---

```{r imports, include=FALSE} 
library(data.table)
library(lmtest)
library(readr)
library(sandwich)
library(stargazer)
library(ggplot2)
``` 

# Load and clean data

```{r read and clean data, results="asis"}
d <- fread("final-project.csv", col.names=c(
  "recipient_name",
  "project_member",
  "profile_name",
  "profile_has_pic",
  "profile_is_male",
  "date_sent",
  "invite_accepted",
  "active_6_mos",
  "recipient_gender",
  "profile_link",
  "last_checked",
  "invite_sent"
))
compliance_rate <- d[, mean(invite_sent, na.rm=TRUE)]
d <- d[!is.na(date_sent) & date_sent != ""]
d <- d[, ':='(
  date_sent = parse_date(date_sent, format="%m/%d/%Y"),
  last_checked = parse_date(last_checked, format="%m/%d/%Y")
)]
d <- d[, invite_days := difftime(last_checked, date_sent, units="day")]
head(d)
```

# Build some models

```{r include=FALSE}
model1 <- d[, lm(invite_accepted ~ profile_has_pic)]
ct1 <- coeftest(model1, vcov=vcovHC)

model2 <- d[, lm(invite_accepted ~ profile_has_pic + profile_is_male + profile_has_pic*profile_is_male)]
ct2 <- coeftest(model2, vcov=vcovHC)

model3 <- d[, lm(invite_accepted ~ profile_has_pic + profile_is_male + profile_has_pic*profile_is_male + active_6_mos + invite_days)]
ct3 <- coeftest(model3, vcov=vcovHC)

model4 <- d[recipient_gender != "na", lm(invite_accepted ~ profile_has_pic + profile_is_male + profile_has_pic*profile_is_male + active_6_mos + invite_days + recipient_gender + profile_is_male * recipient_gender)]
ct4 <- coeftest(model4, vcov=vcovHC)
```

We plan to construct regression models with both single factor and multifactorial designs. This is an example of two such models.

TODO this table needs to be cleaned up to match the rubric

```{r, results="asis"}
stargazer(
  model1, model2, model3, model4,
  header=FALSE,
  title="LinkedIn Experiment Results",
  se = list(ct1[,2], ct2[,2], ct3[,2], ct4[,2]),
  order = c(
    1, 2, 6, 3, 4, 5, 7
  ),
  dep.var.labels=c("Invite Accepted"),
  covariate.labels = c(
    "Treat Picture", 
    "Treat Male",
    "Treat Picture:Treat Male",
    "Inactive 6 Mos",
    "Invite Duration (Days)",
    "Recipient Male",
    "Treat Male:Recipient Male"
  ),
  omit.stat=c("f"),
  notes="All standard errors are robust standard errors."
)
```

# Covariate balance check

We only have one covariate to check: the recipient gender.

TODO should we include "invite_sent"? It's dropped from the data because otherwise we can't 

```{r, results="asis"}
cov1 <- d[, lm(profile_has_pic ~ recipient_gender + active_6_mos)]
cov1$rse <- coeftest(cov1, vcov=vcovHC)
cov2 <- d[, lm(profile_is_male ~ recipient_gender + active_6_mos)]
cov2$rse <- coeftest(cov2, vcov=vcovHC)
stargazer(
  cov1, cov2,
  header=FALSE,
  title="Covariate Balance Test",
  se = list(cov1$rse[,2], cov2$rse[,2]),
  dep.var.labels=c("Treat Picture", "Treat Male"),
  covariate.labels=c(
    "Recipient is Male",
    "Recipient is Unk",
    "Inactive 6 mos"
  ),
  omit.stat=c("f"),
  notes="All standard errors are robust standard errors."
)
```

Test covariate balance for the "invite_sent" variable. This requires us to reload 
the data since we've already filtered out non-compliance at this point.

```{r, results="asis"}
dcov <- fread("final-project.csv", col.names=c(
  "recipient_name",
  "project_member",
  "profile_name",
  "profile_has_pic",
  "profile_is_male",
  "date_sent",
  "invite_accepted",
  "active_6_mos",
  "recipient_gender",
  "profile_link",
  "last_checked",
  "invite_sent"
))
dcov <- dcov[!is.na(invite_sent)]

cov3 <- dcov[, lm(profile_has_pic ~ invite_sent)]
cov3$rse <- coeftest(cov3, vcov=vcovHC)
cov4 <- dcov[, lm(profile_is_male ~ invite_sent)]
cov4$rse <- coeftest(cov4, vcov=vcovHC)
stargazer(
  cov3, cov4,
  header=FALSE,
  title="Covariate Balance Test for Compliance",
  se = list(cov3$rse[,2], cov4$rse[,2]),
  dep.var.labels=c("Treat Picture", "Treat Male"),
  covariate.labels=c(
    "Sent Invite Successfully"
  ),
  omit.stat=c("f"),
  notes="All standard errors are robust standard errors."
)
```

# Graph the invite lag

```{r}
days <- data.table(invite_days_num=seq(0,36))
invite_cumulative <- d[, .(invite_days_num=as.numeric(invite_days), sum=sum(invite_accepted)), by=invite_days]
invite_cumulative <- merge(days, invite_cumulative, by="invite_days_num", all.x=TRUE)
invite_cumulative[is.na(invite_cumulative)] <- 0
invite_cumulative[, cumsum := cumsum(sum)]
```

```{r}
ggplot(data=invite_cumulative, aes(x=invite_days_num, y=cumsum)) +
  geom_col() + 
  ggtitle("How long does it take to accept an invite?") +
  xlab("Days Elapsed Since Invite") + 
  ylab("Accepted Invitations (Cumulative)") +
  scale_y_continuous(breaks=(seq(0,800,200))) +
  theme_light()
```
